---
title: "climate_change"
author: "Dongyoung Kim"
date: "2024-01-02"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
    latex_engine: xelatex
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

# Possible Variables to Extract
```{r}
library(knitr)
names <- c("user_name", "dates", "time", "word_count", "bytes", "chpater", "tag", "comments", "actual_text")
df <- data.frame(Names = names)
kable(df)
```

# Parsing Ideas
## User name
### Corresponding HTML codes

```html
<a href="/wiki/User:Clayoquot" class="mw-userlink" title="User:Clayoquot" data-mw-revid="1190970117"><bdi>Clayoquot</bdi></a>
```
### Idea 
 - Find "User:" and extract the user name
 - Find <bdi></bdi> 

## Dates and Time
### Corresponding HTML codes
```html
<span class="mw-changeslist-time">10:40</span>
<a href="/w/index.php?title=Climate_change&amp;oldid=1190008379" class="mw-changeslist-date" title="Climate change">10:40, 15 December 2023</a>
```
### Idea 
 - Find "mw-changeslist-time" and extract the time
 - Find <bdi></bdi> "class="mw-changeslist-date" title="Climate change">
 
### Python Code
```python
from bs4 import BeautifulSoup

# Your HTML content
html_content = '''
<span class="mw-changeslist-time">10:40</span>
<a href="/w/index.php?title=Climate_change&amp;oldid=1190008379" class="mw-changeslist-date" title="Climate change">10:40, 15 December 2023</a>
'''

# Parse the HTML content
soup = BeautifulSoup(html_content, 'lxml')

# Extract time using the 'mw-changeslist-time' class
time = soup.find(class_="mw-changeslist-time").text

# Extract date using the 'mw-changeslist-date' class
date = soup.find(class_="mw-changeslist-date").text

print(f"Time: {time}")
print(f"Date: {date}")

```

## Word count and Bytes
### Corresponding HTML codes

```html
<span class="history-size mw-diff-bytes" data-mw-bytes="297168">297,168 bytes</span>
<span dir="ltr" class="mw-plusminus-neg mw-diff-bytes" title="299,444 bytes after change of this size">−81</span>
```

### Idea 
 - Find "data-mw-bytes" and extract the bytes
 - Find class="mw-plusminus-neg mw-diff-bytes" and extract bytes and word count
 
## Chapter
### Corresponding HTML codes

```html
<a href="/wiki/Climate_change#Modelling" title="Climate change">→‎Modelling</a>
<span class="autocomment"><a href="/wiki/Climate_change#Modelling" title="Climate change">→‎Modelling</a>: </span>
```
### Idea 

## Tags
### Corresponding HTML codes

```html
<a href="/wiki/Wikipedia:VisualEditor" title="Wikipedia:VisualEditor">Visual edit</a>
```
### Idea 

## Comments
### Corresponding HTML codes

```html
<span dir="auto"><span class="autocomment"><a href="/wiki/Climate_change#Modelling" title="Climate change">→‎Modelling</a>: </span> added wikilinks to GST, although I am struggeling to figure out what exactly should be in the GST article (as to not overlap with all the other articles)</span>
```
### Idea 

## Actual Text
### Corresponding HTML codes
